An open-source integrated framework for the automation of citation collection and screening in systematic reviews.

### 2021-12-13 Manuscript/Manuscript.tex
added abstract and title

\usepackage[utf8]{inputenc} % allow utf-8 input
\usepackage[T1]{fontenc}    % use 8-bit T1 fonts
\usepackage{lmodern}        % https://github.com/rstudio/rticles/issues/343
\usepackage{hyperref}       % hyperlinks
\usepackage{url}            % simple URL typesetting
\usepackage{booktabs}       % professional-quality tables
\usepackage{amsfonts}       % blackboard math symbols
\usepackage{nicefrac}       % compact symbols for 1/2, etc.
\usepackage{microtype}      % microtypography
\usepackage{lipsum}
\usepackage{graphicx}

\title{Main manuscript}

@@

\begin{abstract}
Enter the text of your abstract here.
\end{abstract}

\keywords{
    blah
   \and
    blee
   \and
    bloo
   \and
    these are optional and can be removed
  }

@@

features of the framework.

@@

We built a set of tools to let users automatically search and download
citation data from three major scientific databases (``sources''):
Pubmed (\url{https://pubmed.ncbi.nlm.nih.gov/}), Web Of Science (WOS,
\url{https://apps.webofknowledge.com/}) and the Institute of Electrical
and Electronics Engineers (IEEE,
\url{https://ieeexplore.ieee.org/Xplore/home.jsp}). The framework takes
care of authorization management for non-open databases like WOS and
IEEE. It is also possible to download and import records in the
framework manually; this is particularly useful to acquire records from
the SCOPUS
(\url{https://www.scopus.com/search/form.uri?display=basic\#basic}) and
EMBASE databases
(\url{https://www.embase.com/\#advancedSearch/default}), for which a
comprehensive API interface was not easy to build. An extra manual
search was necessary also for Pubmed, since the API and the web
interface have different rule expansion algorithms and return slightly
different results ({`NCBI Insights : Updated Pubmed e-Utilities Coming
in April 2022!'} n.d.). A short guide on how to set up the framework for
each supported database is available in Supplemental Material S3.\\
The acquired records are merged into a single database, resolving
duplicates and different formatting between sources. The records are
ordered according to the frequency of the positive query terms (e.g.,
not preceded by a \(NOT\) modifier) in the title and abstract (``simple
query ordering'').\\
The researcher is then asked to label a number of records to create the
``initial training set'' needed to start the automatic classification.
We suggest manually labelling the first 250 records (see
``hyperparameter optimization'' later). The simple query ordering
increases the positivity rate in the initial training set (Wallace,
Small, et al. 2010), which provide higher sensitivity during automatic
classification (Chawla, Japkowicz, and Kotcz 2004).

@@

The collected citation data have a number of fields characterizing a
scientific publication. The framework models the relevance of a record
based on the following fields: title, abstract, authors, keywords, MESH
terms (Lipscomb 2000). A series of Natural Language Processing (NLP)
techniques (Baeza-Yates, Ribeiro-Neto, and others 1999; Marshall and
Wallace 2019; Ananiadou and McNaught 2006) are employed to transform the
textual information in these fields into features for machine learning
through a bag-of-words approach (Marshall and Wallace 2019). The
processing of free text fields (title, abstract) includes: tokenization
(i.e., extracting the terms), common stopwords (i.e., sentence
components bringing no meaning) removal, part-of-speech filtering (only
nouns, adjectives, verbs and untagged terms are retained), and
lemmatization of the terms (i.e., reduction to their base grammar form).
Text processing for authors, keywords and MESH terms identifies logical
units (e.g., author's full names, composite keywords) and extracts
them.\\
Terms appearing in less than 5\% of the labelled documents are removed
from negative records. All terms in the positive set are kept to
increase sensitivity at the cost of specificity.\\
Some terms tend to co-appear in records (non-consecutive ngrams,
nc-ngrams), often carrying a particular meaning when copresent. To
detect nc-ngrams, we generated a word network representation (Francois
Rousseau 2015) posing edges between terms with a cosine similarity in
terms of record co-occurrence \textgreater{} 0.5. We extracted the
maximal cliques in the network (Eppstein, Löffler, and Strash 2010)
representing highly correlated groups of terms; These groups of terms
are added to the data set as individual features. Only nc-ngrams
comprising a maximum of ten terms are kept.\\
A second network is built using a co-occurrence threshold of 0.9. In
this case, the cliques represent terms that always appear together and
therefore can be considered redundant (i.e., they do not need to be
considered separately). These terms are merged to increase computation
efficiency and reduce overfitting.\\
The output is a Document-Term Matrix (DTM), with \(N_d\) rows
representing the records (\(D_i\)), \(N_t\) terms column for the
\(t_{field}\) terms (divided by record field) and \({0,1}\) values
whether \(t_{field} \in D_i\). We also enriched the DTM with features
referencing the number of terms in each field to help the model scale
term importance based on the field length.

@@

To evaluate the hyperparameter effect of performance, we set up a ``grid
search'' (Claesen and De Moor 2015; L. Yang and Shami 2020) on a
prelabelled ``validation set'' made of the first 1200 records from the
first session dataset. The framework tested each hyperparameter
combination until four CR iterations with no positive records were
returned or the whole dataset got labelled.\\
For each combination, a performance score was computed as the product of
``Efficiency'' (1 minus the ratio of records that required review over
the total) and ``Sensitivity'' (number of positive records found over
the total of positives). We then identified homogeneous ``performance
clusters'' of scores given hyperparameter values using a partition tree
(Therneau and Atkinson 2019). For the rest of the study, we used the
best hyperparameter set in terms of Sensitivity followed by Efficiency
from the cluster with the highest average score.

@@

The first search session returned a total of 27600 unique records,
specifically 12719 (71.6\% of the total) records from the EMBASE
database, followed by 9546 (53.8\%) from Pubmed, 3175 (17.9\%) from
SCOPUS, 2100 (11.8\%) from WOS, and 60 (0.34\%) from IEEE (Table 1).
There were various degrees of overlapping between sources, with the
38.4\% of records being present in more than one database and EMBASE and
IEEE being the databases with the higher uniqueness ratios. The final
dataset was composed by 17755 unique records.\\
The first 250 records were manually labeled. Of these 43 (17.2\%) were
labeled as positive, and 207 (82.8\%) as negative.

@@

\caption{\label{tab:session 1}\textbf{Table 1}. Distribution of retrieved records by source and session. For each source it is reported the number of records, percentage over the session total (after removing duplicates)' and, number or records specific for a source as absolute value and as percentage over the source total. All session shows records after joining and deduplication of the Session 1 and Session 2 dataset.}
\centering
\resizebox{\linewidth}{!}{
\begin{tabular}[t]{llrlrl}
\toprule
Session & Source & Records & \% over total & Source specific records & \% over source total\\
\midrule
\cellcolor{gray!6}{Session1} & \cellcolor{gray!6}{Total} & \cellcolor{gray!6}{17755} & \cellcolor{gray!6}{} & \cellcolor{gray!6}{} & \cellcolor{gray!6}{}\\
 & Embase & 12719 & 71.6\% & 6683 & 52.5\%\\
\cellcolor{gray!6}{} & \cellcolor{gray!6}{Pubmed} & \cellcolor{gray!6}{9546} & \cellcolor{gray!6}{53.8\%} & \cellcolor{gray!6}{3457} & \cellcolor{gray!6}{36.2\%}\\
 & Scopus & 3175 & 17.9\% & 298 & 9.39\%\\
\cellcolor{gray!6}{} & \cellcolor{gray!6}{WOS} & \cellcolor{gray!6}{2100} & \cellcolor{gray!6}{11.8\%} & \cellcolor{gray!6}{473} & \cellcolor{gray!6}{22.5\%}\\
\addlinespace
 & IEEE & 60 & 0.34\% & 29 & 48.3\%\\
\cellcolor{gray!6}{Session2} & \cellcolor{gray!6}{Total} & \cellcolor{gray!6}{82579} & \cellcolor{gray!6}{} & \cellcolor{gray!6}{} & \cellcolor{gray!6}{}\\
 & Embase & 48396 & 58.6\% & 40826 & 84.4\%\\
\cellcolor{gray!6}{} & \cellcolor{gray!6}{Pubmed} & \cellcolor{gray!6}{28811} & \cellcolor{gray!6}{34.9\%} & \cellcolor{gray!6}{18021} & \cellcolor{gray!6}{62.5\%}\\
 & Scopus & 17070 & 20.7\% & 4908 & 28.8\%\\
\addlinespace
\cellcolor{gray!6}{} & \cellcolor{gray!6}{WOS} & \cellcolor{gray!6}{12956} & \cellcolor{gray!6}{15.7\%} & \cellcolor{gray!6}{2817} & \cellcolor{gray!6}{21.7\%}\\
 & IEEE & 61 & 0.074\% & 22 & 36.1\%\\
\cellcolor{gray!6}{All Sessions} & \cellcolor{gray!6}{Total} & \cellcolor{gray!6}{98371} & \cellcolor{gray!6}{} & \cellcolor{gray!6}{} & \cellcolor{gray!6}{}\\
 & Embase & 59604 & 60.6\% & 46942 & 78.8\%\\
\cellcolor{gray!6}{} & \cellcolor{gray!6}{Pubmed} & \cellcolor{gray!6}{37278} & \cellcolor{gray!6}{37.9\%} & \cellcolor{gray!6}{21371} & \cellcolor{gray!6}{57.3\%}\\
\addlinespace
 & Scopus & 19353 & 19.7\% & 5181 & 26.8\%\\
\cellcolor{gray!6}{} & \cellcolor{gray!6}{WOS} & \cellcolor{gray!6}{14367} & \cellcolor{gray!6}{14.6\%} & \cellcolor{gray!6}{3175} & \cellcolor{gray!6}{22.1\%}\\
 & IEEE & 108 & 0.11\% & 48 & 44.4\%\\
\bottomrule
\end{tabular}}
\end{table}

Records were joined into a database and arrange by simple query
ordering; of these, the first 250 records were labelled to create the
initial training set.\\
Using the classification model,7 automatic classification and manual
review iterations (CR) were performed (Table 2). It is possible to
observe how the number of records that required manual review dropped
rapidly between iterations, indicating that the engine was converging
while the uncertainties were resolved.\\
This phenomenon is better depicted in Fig. 1 of the Supplemental
Material S2. It shows the mixture distribution of the PPD of the
records, specifically for the reviewed positive and negative records,
and for records that need manual review after the classification step:
it can be noticed how the distribution of the uncertain records shrinks
(they concentrate in a shorter probability range) and shifts toward the
negative zone as more positive matches are found and reviewed.
Accordingly (Table 2), the number of new positives found drops after the
first couple of iterations. As per default, the classification process
was stopped after four rounds with no new positive matches; a total
number of 101 positives were found over 766 manually reviewed records
(13.2\% positivity rate).\\

@@

\caption{\label{tab:session 1}\textbf{Table 2}. Results of the automatic classifaction and manual review rounds. For each iteration, the cumulative number of positives and negative records and their sum (Total labelled) and percentage over total are shown. Also, the number of changes after review and their description is reported."Unlab." indicates unlabelled records marked for review. For each Iteration, also the number of features used by the engine is reported. The first row reports the results of the initial manual labelling of records, which acted as input for the automatic classification in Iteration 1. In Session 2, the engine uses the labels at the end of Session 1 to classify the newly added records.}
\centering
\resizebox{\linewidth}{!}{
\begin{tabular}[t]{llrrlrrrrrr}
\toprule
Session & Iteration & Positives & Negatives & Total labelled (\%) & Unlab. -> y & Unlab. -> n & Unlab. -> * & n -> y & Changes & N. features\\
\midrule
\cellcolor{gray!6}{Session1 (n = 17755)} & \cellcolor{gray!6}{Initial labelling} & \cellcolor{gray!6}{43} & \cellcolor{gray!6}{207} & \cellcolor{gray!6}{250 (1.41\%)} & \cellcolor{gray!6}{43} & \cellcolor{gray!6}{207} & \cellcolor{gray!6}{0} & \cellcolor{gray!6}{0} & \cellcolor{gray!6}{250} & \cellcolor{gray!6}{2289}\\
 & 1 & 93 & 529 & 622 (3.5\%) & 50 & 322 & 0 & 0 & 372 & 2289\\
\cellcolor{gray!6}{} & \cellcolor{gray!6}{2} & \cellcolor{gray!6}{100} & \cellcolor{gray!6}{614} & \cellcolor{gray!6}{714 (4.02\%)} & \cellcolor{gray!6}{6} & \cellcolor{gray!6}{86} & \cellcolor{gray!6}{0} & \cellcolor{gray!6}{1} & \cellcolor{gray!6}{93} & \cellcolor{gray!6}{3750}\\
 & 3 & 101 & 625 & 726 (4.09\%) & 1 & 11 & 0 & 0 & 12 & 3834\\
\cellcolor{gray!6}{} & \cellcolor{gray!6}{4} & \cellcolor{gray!6}{101} & \cellcolor{gray!6}{648} & \cellcolor{gray!6}{749 (4.22\%)} & \cellcolor{gray!6}{0} & \cellcolor{gray!6}{23} & \cellcolor{gray!6}{0} & \cellcolor{gray!6}{0} & \cellcolor{gray!6}{23} & \cellcolor{gray!6}{3856}\\
\addlinespace
 & 5 & 101 & 651 & 752 (4.24\%) & 0 & 3 & 0 & 0 & 3 & 3856\\
\cellcolor{gray!6}{} & \cellcolor{gray!6}{6} & \cellcolor{gray!6}{101} & \cellcolor{gray!6}{660} & \cellcolor{gray!6}{761 (4.29\%)} & \cellcolor{gray!6}{0} & \cellcolor{gray!6}{9} & \cellcolor{gray!6}{0} & \cellcolor{gray!6}{0} & \cellcolor{gray!6}{9} & \cellcolor{gray!6}{3856}\\
 & 7 & 101 & 665 & 766 (4.31\%) & 0 & 5 & 0 & 0 & 5 & 3856\\
\cellcolor{gray!6}{Session2 (n = 98371)} & \cellcolor{gray!6}{1} & \cellcolor{gray!6}{106} & \cellcolor{gray!6}{934} & \cellcolor{gray!6}{1040 (1.06\%)} & \cellcolor{gray!6}{5} & \cellcolor{gray!6}{270} & \cellcolor{gray!6}{998} & \cellcolor{gray!6}{0} & \cellcolor{gray!6}{1273} & \cellcolor{gray!6}{4729}\\
 & 2 & 107 & 1123 & 1230 (1.25\%) & 1 & 189 & 0 & 0 & 190 & 4729\\
\addlinespace
\cellcolor{gray!6}{} & \cellcolor{gray!6}{3} & \cellcolor{gray!6}{107} & \cellcolor{gray!6}{1176} & \cellcolor{gray!6}{1283 (1.3\%)} & \cellcolor{gray!6}{0} & \cellcolor{gray!6}{53} & \cellcolor{gray!6}{0} & \cellcolor{gray!6}{0} & \cellcolor{gray!6}{53} & \cellcolor{gray!6}{4733}\\
 & 4 & 107 & 1200 & 1307 (1.33\%) & 0 & 24 & 0 & 0 & 24 & 4729\\
\cellcolor{gray!6}{} & \cellcolor{gray!6}{5} & \cellcolor{gray!6}{107} & \cellcolor{gray!6}{1209} & \cellcolor{gray!6}{1316 (1.34\%)} & \cellcolor{gray!6}{0} & \cellcolor{gray!6}{9} & \cellcolor{gray!6}{0} & \cellcolor{gray!6}{0} & \cellcolor{gray!6}{9} & \cellcolor{gray!6}{4729}\\
 & 6 & 107 & 1226 & 1333 (1.36\%) & 0 & 17 & 0 & 0 & 17 & 4729\\
\bottomrule
\end{tabular}}
\end{table}

By evaluating how often a term was used by the classification model, it
is possible to define their relevance in labeling the records (see
Methods). Here follows the 15 most relevant terms by inclusion rate over
10,000 posterior tree inclusions, described as: Term (citation part):
Inclusion Rate (Inclusion Stability) {[}linear Relative Risk,
Statistic{]}.

@@

The ``\&'' indicates nc-ngrams, i.e., terms strongly co-occurrent in the
documents.\\
The engine was able to pick up the central concept of the research,
i.e., ``patient transport'' or ``transfer'' through a ``network'' of
``facility''ies that facilitates the ``spread'' of infections, and even
one of the authors of this study (Donker T.) or the region of interest
(``Orange County'') of another research group active on the topic of
healthcare asociated pathogen spreading over hospital networks. It is
interesting to see that some terms were considered highly relevant for
the BART models (e.g., ``Worker'' in 6th position out of more than 3800
terms considered) although in a simpler linear model their effect would
be hardly significant (statistic: -1.21 s.e.); these are terms which are
relevant only together with other terms but not by themselves,
highlighting the extra predictive power brought by a non-linear model
like BART.\\
A more extensive set of terms is presented in Table 1 of Supplemental
Material S2.

@@

The field of literature review automatisation is mature and ripe with
innovation, and we expect an increasing use of such technologies to
confront the ever-faster production of scientific literature. We believe
it is appreciable that a multiplicity of tools are being made available
to let researchers and policymakers find the instrument that better fits
their needs.\\
We tried to contribute to the field with an innovative methodology and
tool that provides excellent performance and easy integration with
existing systematic review pipelines. The value of this work lies not
only in the framework itself, which we provide as open-source software,
but in the set of solutions we developed to solve various SRA issues and
that can be used to improve existing solutions.

>>>>

\usepackage[utf8]{inputenc} % allow utf-8 input
\usepackage[T1]{fontenc}    % use 8-bit T1 fonts
\usepackage{lmodern}        % https://github.com/rstudio/rticles/issues/343
\usepackage{hyperref}       % hyperlinks
\usepackage{url}            % simple URL typesetting
\usepackage{booktabs}       % professional-quality tables
\usepackage{amsfonts}       % blackboard math symbols
\usepackage{nicefrac}       % compact symbols for 1/2, etc.
\usepackage{microtype}      % microtypography
\usepackage{graphicx}

\title{An open-source integrated framework for the automation of
citation collection and screening in systematic reviews.}

@@

\begin{abstract}
The exponential growth in scientific production makes its summarisation
through secondary literature exceedingly demanding in terms of time and
human resources. We introduce a new open-source framework that
significantly increases efficiency during the citation collection and
screening phases of systematic reviews.\\
The framework introduces three main tools: an automatic citation search
engine and manager that allows collecting records from multiple citation
databases (PUBMED, WOS, SCOPUS, EMBASE, IEEE) with a unified query
syntax; a citation screening tool based on Bayesian active machine
learning and natural language processing, which requires users feedback
only on uncertain classifications to increase predictive accuracy
iteratively; a semi-automatic data-driven query generator to create new
search queries from existing reviewed citation data sets.\\
The framework was applied on an example topic performing citation
collection and screening. We estimated median posterior Sensitivity and
Efficiency {[}90\% Credible Intervals{]} using Bayesian simulation to
predict the distribution of possibly missed relevant matches in the
unreviewed records.\\
17755 unique records were collected through the framework citation
manager; 101 over 766 records were found to be relevant after manual
evaluation, while the rest were excluded by the automatic
classification; the expected Efficiency was 95.7\% {[}95.3\%, 95.7\%{]}
for a Sensitivity of 100\% {[}93.5\%, 100\%{]}. A new search query was
generated from the labelled dataset, and 82579 more records were
collected. Only 567 records required human review after the automatic
screening, and six additional positive matches were found. Including the
additional records, the overall expected Sensitivity dropped to 97.3\%
{[}73.8\%, 100\%{]} while the Efficiency raised to 98.6\% {[}98.2\%,
98.7\%{]}.\\
The framework can significantly reduce human resources requirements for
systematic reviews by simplifying citation collection and screening
while demonstrating exceptional sensitivity even on large data sets.
\end{abstract}

\keywords{
    Systematic review automation
   \and
    Citation management
   \and
    Online data collection
   \and
    Active machine learning
   \and
    Natural language processing
   \and
    Bayesian modeling
  }

@@

features of the framework.\\

@@

We built a set of tools to let users automatically search and download
citation data from three major scientific databases (``sources''):
Pubmed (\url{https://pubmed.ncbi.nlm.nih.gov/}), Web Of Science (WOS,
\url{https://apps.webofknowledge.com/}) and the Institute of Electrical
and Electronics Engineers (IEEE,
\url{https://ieeexplore.ieee.org/Xplore/home.jsp}). The framework takes
care of authorization management for non-open databases like WOS and
IEEE. It is also possible to download and import records in the
framework manually; this is particularly useful to acquire records from
the SCOPUS (\url{https://www.scopus.com/}) and EMBASE databases
(\url{https://www.embase.com/}), for which a comprehensive API interface
was not easy to build. An extra manual search was necessary also for
Pubmed, since the API and the web interface have different rule
expansion algorithms and return slightly different results ({`NCBI
Insights : Updated Pubmed e-Utilities Coming in April 2022!'} n.d.). A
short guide on how to set up the framework for each supported database
is available in Supplemental Material S3.\\
The acquired records are merged into a single database, resolving
duplicates and different formatting between sources. The records are
ordered according to the frequency of the positive query terms (e.g.,
not preceded by a \(NOT\) modifier) in the title and abstract (``simple
query ordering'').\\
The researcher is then asked to label a number of records to create the
``initial training set'' needed to start the automatic classification.
We suggest manually labelling the first 250 records (see
``hyperparameter optimization'' later). The simple query ordering
increases the positivity rate in the initial training set (Wallace,
Small, et al. 2010), which provide higher sensitivity during automatic
classification (Chawla, Japkowicz, and Kotcz 2004).

@@

The collected citation data have a number of fields characterising a
scientific publication. The framework models the relevance of a record
based on the following fields: title, abstract, authors, keywords, MESH
terms (Lipscomb 2000). A series of Natural Language Processing (NLP)
techniques (Baeza-Yates, Ribeiro-Neto, and others 1999; Marshall and
Wallace 2019; Ananiadou and McNaught 2006) are employed to transform the
textual information in these fields into features for machine learning
through a bag-of-words approach (Marshall and Wallace 2019). The
processing of free text fields (title, abstract) includes: tokenization
(i.e., extracting the terms), common stopwords (i.e., sentence
components bringing no meaning) removal, part-of-speech filtering (only
nouns, adjectives, verbs and untagged terms are retained), and
lemmatization of the terms (i.e., reduction to their base grammar form).
Text processing for authors, keywords and MESH terms identifies logical
units (e.g., author's full names, composite keywords) and extracts
them.\\
Terms appearing in less than 5\% of the labelled documents are removed
from negative records. All terms in the positive set are kept to
increase sensitivity at the cost of specificity.\\
Some terms tend to co-appear in records (non-consecutive ngrams,
nc-ngrams), often carrying a particular meaning when copresent. To
detect nc-ngrams, we generated a word network representation (Francois
Rousseau 2015) posing edges between terms with a cosine similarity in
terms of record co-occurrence \textgreater{} 0.5. We extracted the
maximal cliques in the network (Eppstein, Löffler, and Strash 2010)
representing highly correlated groups of terms; These groups of terms
are added to the data set as individual features. Only nc-ngrams
comprising a maximum of ten terms are kept.\\
A second network is built using a co-occurrence threshold of 0.9. In
this case, the cliques represent terms that always appear together and
therefore can be considered redundant (i.e., they do not need to be
considered separately). These terms are merged to increase computation
efficiency and reduce overfitting.\\
The output is a Document-Term Matrix (DTM), with \(N_d\) rows
representing the records (\(D_i\)), \(N_t\) terms column for the
\(t_{field}\) terms (divided by record field) and \({0,1}\) values
whether \(t_{field} \in D_i\). We also enriched the DTM with features
referencing the number of terms in each field to help the model scale
term importance based on the field length.

@@

To evaluate the hyperparameter effect of performance, we set up a ``grid
search'' (Claesen and De Moor 2015; L. Yang and Shami 2020) on a
prelabelled ``validation set'' made of the first 1200 records from the
first session data set. The framework tested each hyperparameter
combination until four CR iterations with no positive records were
returned or the whole data set got labelled.\\
For each combination, a performance score was computed as the product of
``Efficiency'' (1 minus the ratio of records that required review over
the total) and ``Sensitivity'' (number of positive records found over
the total of positives). We then identified homogeneous ``performance
clusters'' of scores given hyperparameter values using a partition tree
(Therneau and Atkinson 2019). For the rest of the study, we used the
best hyperparameter set in terms of Sensitivity followed by Efficiency
from the cluster with the highest average score.\\

@@

The first search session returned a total of 27600 records, specifically
12719 (71.6\% of the total) records from the EMBASE database, followed
by 9546 (53.8\%) from Pubmed, 3175 (17.9\%) from SCOPUS, 2100 (11.8\%)
from WOS, and 60 (0.34\%) from IEEE (Table 1). There were various
degrees of overlapping between sources, with the 38.4\% of records being
present in more than one database and EMBASE and IEEE being the
databases with the higher uniqueness ratios. The final data set was
composed by 17755 unique records.\\
The first 250 records (based on ``simple query ordering'') were manually
labeled. Of these 43 (17.2\%) were labeled as positive, and 207 (82.8\%)
as negative.

@@

\caption{\label{tab:Table 1}\textbf{Table 1}. Distribution of retrieved records by source and session. For each source it is reported the number of records, percentage over the session total (after removing duplicates), and number or records specific for a source as absolute value and as percentage over the source total. All session shows records after joining and deduplication of the Session 1 and Session 2 data set.}
\centering
\resizebox{\linewidth}{!}{
\begin{tabular}[t]{llrlrl}
\toprule
Session & Source & Records & \% over total & Source specific records & \% over source total\\
\midrule
\cellcolor{gray!6}{Session1} & \cellcolor{gray!6}{Total} & \cellcolor{gray!6}{17755} & \cellcolor{gray!6}{} & \cellcolor{gray!6}{} & \cellcolor{gray!6}{}\\
 & Embase & 12719 & 71.6\% & 6683 & 52.5\%\\
\cellcolor{gray!6}{} & \cellcolor{gray!6}{Pubmed} & \cellcolor{gray!6}{9546} & \cellcolor{gray!6}{53.8\%} & \cellcolor{gray!6}{3457} & \cellcolor{gray!6}{36.2\%}\\
 & Scopus & 3175 & 17.9\% & 298 & 9.39\%\\
\cellcolor{gray!6}{} & \cellcolor{gray!6}{WOS} & \cellcolor{gray!6}{2100} & \cellcolor{gray!6}{11.8\%} & \cellcolor{gray!6}{473} & \cellcolor{gray!6}{22.5\%}\\
\addlinespace
 & IEEE & 60 & 0.34\% & 29 & 48.3\%\\
\cellcolor{gray!6}{Session2} & \cellcolor{gray!6}{Total} & \cellcolor{gray!6}{82579} & \cellcolor{gray!6}{} & \cellcolor{gray!6}{} & \cellcolor{gray!6}{}\\
 & Embase & 48396 & 58.6\% & 40826 & 84.4\%\\
\cellcolor{gray!6}{} & \cellcolor{gray!6}{Pubmed} & \cellcolor{gray!6}{28811} & \cellcolor{gray!6}{34.9\%} & \cellcolor{gray!6}{18021} & \cellcolor{gray!6}{62.5\%}\\
 & Scopus & 17070 & 20.7\% & 4908 & 28.8\%\\
\addlinespace
\cellcolor{gray!6}{} & \cellcolor{gray!6}{WOS} & \cellcolor{gray!6}{12956} & \cellcolor{gray!6}{15.7\%} & \cellcolor{gray!6}{2817} & \cellcolor{gray!6}{21.7\%}\\
 & IEEE & 61 & 0.074\% & 22 & 36.1\%\\
\cellcolor{gray!6}{All Sessions} & \cellcolor{gray!6}{Total} & \cellcolor{gray!6}{98371} & \cellcolor{gray!6}{} & \cellcolor{gray!6}{} & \cellcolor{gray!6}{}\\
 & Embase & 59604 & 60.6\% & 46942 & 78.8\%\\
\cellcolor{gray!6}{} & \cellcolor{gray!6}{Pubmed} & \cellcolor{gray!6}{37278} & \cellcolor{gray!6}{37.9\%} & \cellcolor{gray!6}{21371} & \cellcolor{gray!6}{57.3\%}\\
\addlinespace
 & Scopus & 19353 & 19.7\% & 5181 & 26.8\%\\
\cellcolor{gray!6}{} & \cellcolor{gray!6}{WOS} & \cellcolor{gray!6}{14367} & \cellcolor{gray!6}{14.6\%} & \cellcolor{gray!6}{3175} & \cellcolor{gray!6}{22.1\%}\\
 & IEEE & 108 & 0.11\% & 48 & 44.4\%\\
\bottomrule
\end{tabular}}
\end{table}

The labeled records were used to train the Bayesian classification model
used to label the remaining records. After seven classification and
review (CR) iterations (three resulting in new positive matches and four
extra replications to account for stochastic variability), a total of
101 positives matches were found, requiring manual review of 766 records
(13.2\% positivity rate).\\
It is possible to observe how the number of records that required manual
review dropped rapidly between iterations (Table 2), indicating that the
engine was converging while the uncertainties were resolved.\\
This phenomenon is better depicted in Fig. 1 of the Supplemental
Material S2, showing the mixture distribution of the PPDs of the
records, specifically for the reviewed positive and negative records,
and for records that need manual review after the classification step:
it can be noticed how the distribution of the uncertain records shrinked
(they concentrate in a shorter probability range) and shifted toward the
negative zone as more positive matches are found and reviewed.

@@

\caption{\label{tab:Table 2}\textbf{Table 2}. Results of the automatic classifaction and manual review rounds. For each iteration, the cumulative number of positives and negative records and their sum (Total labelled) and percentage over total are shown. Also, the number of changes after review and their description is reported."Unlab." indicates unlabelled records marked for review. For each Iteration, also the number of features used by the engine is reported. The first row reports the results of the initial manual labelling of records, which acted as input for the automatic classification in Iteration 1. In Session 2, the engine uses the labels at the end of Session 1 to classify the newly added records.}
\centering
\resizebox{\linewidth}{!}{
\begin{tabular}[t]{llrrlrrrrrr}
\toprule
Session & Iteration & Positives & Negatives & Total labelled (\%) & Unlab. -> y & Unlab. -> n & Unlab. -> * & n -> y & Changes & N. features\\
\midrule
\cellcolor{gray!6}{Session1 (n = 17755)} & \cellcolor{gray!6}{Initial labelling} & \cellcolor{gray!6}{43} & \cellcolor{gray!6}{207} & \cellcolor{gray!6}{250 (1.41\%)} & \cellcolor{gray!6}{43} & \cellcolor{gray!6}{207} & \cellcolor{gray!6}{0} & \cellcolor{gray!6}{0} & \cellcolor{gray!6}{250} & \cellcolor{gray!6}{2289}\\
 & 1 & 93 & 529 & 622 (3.5\%) & 50 & 322 & 0 & 0 & 372 & 2289\\
\cellcolor{gray!6}{} & \cellcolor{gray!6}{2} & \cellcolor{gray!6}{100} & \cellcolor{gray!6}{614} & \cellcolor{gray!6}{714 (4.02\%)} & \cellcolor{gray!6}{6} & \cellcolor{gray!6}{86} & \cellcolor{gray!6}{0} & \cellcolor{gray!6}{1} & \cellcolor{gray!6}{93} & \cellcolor{gray!6}{3750}\\
 & 3 & 101 & 625 & 726 (4.09\%) & 1 & 11 & 0 & 0 & 12 & 3834\\
\cellcolor{gray!6}{} & \cellcolor{gray!6}{4} & \cellcolor{gray!6}{101} & \cellcolor{gray!6}{648} & \cellcolor{gray!6}{749 (4.22\%)} & \cellcolor{gray!6}{0} & \cellcolor{gray!6}{23} & \cellcolor{gray!6}{0} & \cellcolor{gray!6}{0} & \cellcolor{gray!6}{23} & \cellcolor{gray!6}{3856}\\
\addlinespace
 & 5 & 101 & 651 & 752 (4.24\%) & 0 & 3 & 0 & 0 & 3 & 3856\\
\cellcolor{gray!6}{} & \cellcolor{gray!6}{6} & \cellcolor{gray!6}{101} & \cellcolor{gray!6}{660} & \cellcolor{gray!6}{761 (4.29\%)} & \cellcolor{gray!6}{0} & \cellcolor{gray!6}{9} & \cellcolor{gray!6}{0} & \cellcolor{gray!6}{0} & \cellcolor{gray!6}{9} & \cellcolor{gray!6}{3856}\\
 & 7 & 101 & 665 & 766 (4.31\%) & 0 & 5 & 0 & 0 & 5 & 3856\\
\cellcolor{gray!6}{Session2 (n = 98371)} & \cellcolor{gray!6}{1} & \cellcolor{gray!6}{106} & \cellcolor{gray!6}{934} & \cellcolor{gray!6}{1040 (1.06\%)} & \cellcolor{gray!6}{5} & \cellcolor{gray!6}{270} & \cellcolor{gray!6}{998} & \cellcolor{gray!6}{0} & \cellcolor{gray!6}{1273} & \cellcolor{gray!6}{4729}\\
 & 2 & 107 & 1123 & 1230 (1.25\%) & 1 & 189 & 0 & 0 & 190 & 4729\\
\addlinespace
\cellcolor{gray!6}{} & \cellcolor{gray!6}{3} & \cellcolor{gray!6}{107} & \cellcolor{gray!6}{1176} & \cellcolor{gray!6}{1283 (1.3\%)} & \cellcolor{gray!6}{0} & \cellcolor{gray!6}{53} & \cellcolor{gray!6}{0} & \cellcolor{gray!6}{0} & \cellcolor{gray!6}{53} & \cellcolor{gray!6}{4733}\\
 & 4 & 107 & 1200 & 1307 (1.33\%) & 0 & 24 & 0 & 0 & 24 & 4729\\
\cellcolor{gray!6}{} & \cellcolor{gray!6}{5} & \cellcolor{gray!6}{107} & \cellcolor{gray!6}{1209} & \cellcolor{gray!6}{1316 (1.34\%)} & \cellcolor{gray!6}{0} & \cellcolor{gray!6}{9} & \cellcolor{gray!6}{0} & \cellcolor{gray!6}{0} & \cellcolor{gray!6}{9} & \cellcolor{gray!6}{4729}\\
 & 6 & 107 & 1226 & 1333 (1.36\%) & 0 & 17 & 0 & 0 & 17 & 4729\\
\bottomrule
\end{tabular}}
\end{table}

We extracted the 15 term more relevant for the classification model,
described as: Term (citation part): Inclusion Rate (Inclusion Stability)
{[}linear Relative Risk, Statistic{]}.

@@

The ``\&'' indicates nc-ngrams, i.e., terms strongly co-occurrent in the
documents.\\
The engine was able to pick up the central concept of the research,
i.e., ``patient transport'' or ``transfer'' through a ``network'' of
``facility''ies that facilitates the ``spread'' of infections, and even
one of the authors of this study (Donker T.) as well as the region of
interest (``Orange County'') of another research group active on the
topic of healthcare asociated pathogen spreading over hospital networks.
Some terms were considered highly relevant for the BART models (e.g.,
``Worker'' in 6th position out of more than 3800 terms considered)
although in a simpler linear model their effect would be hardly
significant (statistic: -1.21 s.e.); these are terms which are relevant
only in conjunction with other terms but not by themselves, highlighting
the extra predictive power brought by a non-linear model like BART.\\
A more extensive set of terms is presented in Table 1 of Supplemental
Material S2.

@@

The field of literature review automation is maturing rapidly, and we
expect an increasing use of such technologies to manage the ever-faster
rate of scientific production. We believe it is appreciable that a
multiplicity of tools are being made available to let researchers and
policymakers find the instrument that better fits their needs.\\
We contribute to this field with an innovative framework that provide
excellent performance and easy integration with existing systematic
review pipelines. The value of this work lies not only in the framework
itself, which we provide as open-source software, but in the set of
methodologies we developed to solve various SRA issues and that can be
used to improve already existing solutions.\\
